# Dataset Transformation
 1. Load the files into "R"
 2. Concatenate the training and the test sets
 3. Extract only the measurements on the mean and standard deviation
 4. Use descriptive activity names
 5. label the data set with descriptive variable names
 6. Create a tidy data set

# Tidy Dataset Analysis
## Variables Description
  
Variable name    | Description
-----------------|-------------------------------------------------------------------
SubjectId.Id     | Identifier of the subject who carried out the experiment (1 to 30)
Activity         | Activity label (LAYING, SITTING, ...)
Signal.Domain    | Domain of the signal: Time or frequency (Time or Freq)
Measurement      | Measured variable
#Measurements    | Number of measurements used to compute the "Average"
Mean.Average     | Average of the "Mean value" variable by "Subject", "Activity", "Signal.Domain" and "Measurment"
SD.Average       | Average of the "Standard deviation" variable by "Subject", "Activity", "Signal.Domain" and "Measurment"

## Dataset Dimensions
  
  ```{r}
dim(dtTidy)
```

## Key Variables
  
  ```{r}
key(dtTidy)
```

## Dataset Structure
  
  ```{r}
str(dtTidy)
```

## Variables Summary
  
  ```{r}
summary(dtTidy)
```

## First six rows of the Dataset
  
  ```{r}
head(dtTidy)
```
