# Codebook

## Variable list and descriptions
  
Variable name    | Description
-----------------|-------------------------------------------------------------------
SubjectId.Id     | Identifier of the subject who carried out the experiment (1 to 30)
Activity         | Activity label (LAYING, SITTING, ...)
Signal.Domain    | Domain of the signal: Time or frequency (Time or Freq)
Measurement      | Measured variable
#Measurements    | Number of measurements used to compute the "Average"
Mean.Average     | Average of the "Mean value" variable by "Subject", "Activity", "Signal.Domain" and "Measurment"
SD.Average       | Average of the "Standard deviation" variable by "Subject", "Activity", "Signal.Domain" and "Measurment"

## Dataset dimensions
  
  ```{r}
dim(dtTidy)
```

## Dataset structure
  
  ```{r}
str(dtTidy)
```

## List the key variables in the data table
  
  ```{r}
key(dtTidy)
```

## Show a few rows of the dataset
  
  ```{r}
dtTidy
```

## Summary of variables
  
  ```{r}
summary(dtTidy)
```
